Learning filters from user provided image makers

### 2020-06-03 main.tex
new figures

\usepackage[pdftex]{graphicx}
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{comment}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsfonts}

@@

\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.8\linewidth]{figures/filter.png}
  \end{center}
  \caption{Filter learned from clustering.}
  \label{fig:filter}
\end{figure}

@@

\begin{figure}[t]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/coco_markers.png}
    \end{center}
       \caption{Markers on an image which contains a coconut tree.}
    \label{fig:coco-markers}
  \end{figure}

  \begin{figure}[t]
    \begin{center}
       \includegraphics[width=0.4\linewidth]{figures/non_coco-markers.png}
    \end{center}
       \caption{Markers on an image which does not contain a coconut tree.}
    \label{fig:non-coco-markers}
  \end{figure}

We placed markers on these images in regions that we consider important to identify the coconut and non-coconut (more diverse) classes. An example of a coconut tree image with markers can be seen in Figure \ref{fig:coco-markers} and non-coconut tree image with markers in Figure \ref{fig:non-coco-markers}.

@@

@@

\begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
  Ours & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.85 \pm 0.02$\\
  Ours (fine tuned) & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.84 \pm 0.02$\\
  VGG-16 & $0.84 \pm 0.01$ & $0.76 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  VGG-16 (fine tuned) & $0.84 \pm 0.01$ & $0.75 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Results.}
  \label{tab:results}
\end{table}

>>>>

\usepackage[pdftex]{graphicx}
\ifCLASSOPTIONcompsoc
  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
\else
  \usepackage[caption=false,font=footnotesize]{subfig}
\fi
\usepackage{comment}
\usepackage{float}
\usepackage{mathtools}
\usepackage{amsfonts}
\usepackage{bm}

@@

\begin{comment}
\begin{figure}[t]
  \begin{center}
     \includegraphics[width=0.8\linewidth]{figures/filter.png}
  \end{center}
  \caption{Filter learned from clustering.}
  \label{fig:filter}
\end{figure}
\end{comment}

\begin{figure}[!t]
  \centering
  \subfloat[Groups of three classes centered on the origin.]{\includegraphics[width=.7\linewidth]{figures/example_groups/groups_centered}}
  \\
  \subfloat[Groups after applying convolution and activation operations.]{\includegraphics[width=.7\linewidth]{figures/example_groups/groups3d_centered}
  \label{fig_second_case}}
  \caption{Exemple of application of convolution with groups centers as filters' weightes.}
  \label{fig:filter}
\end{figure}

@@

\begin{figure}[!t]
    \centering
    \subfloat[Markers on an image which contains a coconut tree.]{\includegraphics[width=.45\linewidth]{figures/markers1}
    \label{fig:markers1}}
    ~
    \subfloat[Markers on an image which does not contain a coconut tree.]{\includegraphics[width=.45\linewidth]{figures/markers2}
    \label{fig:markers2}}
    \\
    \subfloat[Markers on an image which does not contain a coconut tree.]{\includegraphics[width=.45\linewidth]{figures/markers3}
    \label{fig:markers3}}
    ~
    \subfloat[Markers on an image which does not contain a coconut tree.]{\includegraphics[width=.45\linewidth]{figures/markers4}
    \label{fig:markers4}}
    \caption{Markers used for training.}
\end{figure}

We placed markers on these images in regions that we consider important to identify the coconut and non-coconut (more diverse) classes. An example of a coconut tree image with markers can be seen in Figure \ref{fig:markers1} and non-coconut tree image with markers in Figure \ref{fig:markers2}.

@@

\begin{figure}
  \centering
  \subfloat[Visualization of original image feature space.]{\includegraphics[width=.45\linewidth]{figures/input}
  \label{fig:vis-input}}
  ~
  \subfloat[Visualization of the feature extractor's outputs.]{\includegraphics[width=.45\linewidth]{figures/feature_extractor}
  \label{fig:vis-feature-extractor}}
  \\
  \subfloat[Visualization of outputs from the last classifier hidden layer.]{\includegraphics[width=.45\linewidth]{figures/classifier}
  \label{fig:vis-classifier}}
  \caption{This image shows visualizations of the input images and the intermediate layer's outputs. Green points represent background images, and red points represent images that have a coconut tree. The projection from high dimensionality space to 2D was made using t-SNE. The original image shows much overlap between the classes; after applying the feature extractor with only one convolutional layer, we can see that the overlapping decreases considerably. Before the decision layer, the last layer put most of the images from one class on one side and the other on the other side.}
\end{figure}

@@

\begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
    Ours & $\boldsymbol{0.86 \pm 0.01}$ & $0.84 \pm 0.02$ & $0.85 \pm 0.02$\\
  Ours (fine tuned) & $0.86 \pm 0.01$ & $0.84 \pm 0.02$ & $0.84 \pm 0.02$\\
  Ours with SVM & $0.81 \pm 0.02$ & $0.77 \pm 0.03$ & $0.78 \pm 0.02$\\
  VGG-16 & $0.84 \pm 0.01$ & $0.76 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  VGG-16 (fine tuned) & $0.84 \pm 0.01$ & $0.75 \pm 0.03$ & $0.77 \pm 0.02 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Results.}
  \label{tab:results}
\end{table}

\section{Conclusions}
